Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-05-10 analysis/paper_draft2.Rmd
Update paper_draft2.Rmd
edits to paper draft text

Figures 1-3 depicts the bias detection of $b_{curr}$ with an 80\%, 90\%, and 95\% credible interval, respectively, for the 7 combinations of $b_{hist}$, and 7 combinations of $b_{curr}$, three different levels the power prior discounting parameter $a$, and different sizes of the historical data ($h = {1,2,3}$).

@@

Figure 1 depicts the coverage rate with an 80\% credible interval. When we place low weight on the historical strike data ($a = 0.1$), we mostly rely on current strike information. When $b_{curr}$ is 3, 2, -2, or -3, the coverage rate is high, very close to 1. However, when $b_{curr} = 1$, the coverage rate drops below 0.8. If the bias is not strong, our model detects it with a lower accuracy.

As we place more weight on the historical strike data (as $a$ increases), when the historical strike data is consistent with current information, the accuracy of detecting the bias is also close to 1 when $b_{curr} = 1$. When $b_{curr} = 0$ (no bias), however, the coverage rate is also around 80\%. Thus, if we use the 80\% credible interval, we have about a 20\% chance of erroneously detecting non-zero bias.

>>>>

@@

Figure 1 depicts the bias detection rate with an 95\% credible interval for the n_strikes = 15 scenario. When $b_{curr}$ is high (close to 3) the coverage rate is high, very close to 1. However, when $b_{curr}$ is lower (close to zero), the bias detection rate drops below 0.8. When there is no bias in the current or historical trials ($b_{curr} = b_{hist} = 0$}), our bias detection rate for 95% CI is 0.05 or less. As we place more weight on the historical strike data (as $a$ increases), and the historical strike data is consistent with current information (high compatibility between current and historical trials, the bias detection rate is close to 1, especially when bias is high (upper right-hand corner of plots). Conversely, as alpha decreases, bias detection is only high when there is high bias in the current trial ($b_{curr} >= 1.5). Increasing the number of historical trails leads to an increase in bias detection especially when current and historical trials are compatible.
